\documentclass[11pt]{article}

% --------------------
% Packages
% --------------------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{tcolorbox}
\tcbuselibrary{documentation, skins}
\usepackage{longtable}
\setstretch{1.1}
\usepackage{tikz}
\usetikzlibrary{positioning,calc,arrows.meta,shapes.geometric}

\newtcolorbox{marker}[1][]{enhanced,
  before skip balanced=2mm,after skip balanced=3mm,
  boxrule=0.4pt,left=5mm,right=2mm,top=1mm,bottom=1mm,
  colback=yellow!10,
  sharp corners,rounded corners=southeast,arc is angular,arc=3mm,
  underlay={%
    \path[fill=tcbcolback!80!black] ([yshift=3mm]interior.south east)--++(-0.4,-0.1)--++(0.1,-0.2);
    \path[draw=tcbcolframe,shorten <=-0.05mm,shorten >=-0.05mm] ([yshift=3mm]interior.south east)--++(-0.4,-0.1)--++(0.1,-0.2);
    \path[fill=tcbcolback!80!black,draw=none] (interior.south west) rectangle node{\large\bfseries {#1}} ([xshift=4mm]interior.north west);
    },
  drop fuzzy shadow}

\newenvironment{commentbox}[1][]{
  \small
  \begin{marker}[\faChessPawn{}]
    {\textbf{#1}}
  }{
  \end{marker}
}

\newenvironment{surprisebox}[1][]{
  \small
  \begin{marker}[\faChessKnight{}]
    {\textbf{#1}}
  }{
  \end{marker}
}

\newenvironment{examplebox}[1][]{
  \small
  \begin{marker}[\faChessBishop{}]
    {\textbf{#1}}
  }{
  \end{marker}
}

\newenvironment{questionbox}[1][]{
  \small
  \begin{marker}[\faChessRook{}]
    {\textbf{#1}}
  }{
  \end{marker}
}

\newenvironment{keybox}[1][]{
\small
  \begin{marker}[\faChessQueen{}]
    {\textbf{#1}}
  }{
  \end{marker}
}

\newenvironment{warningbox}[1][]{
  \small
  \begin{marker}[\faChessKing{}]
    {\textbf{#1}}
  }{
  \end{marker}
}

\newcommand{\code}{\texttt}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
%\def\Section{\S}
\newcommand{\Section}{\textsection}

\renewcommand{\figureautorefname}{Fig.}
\renewcommand{\tableautorefname}{Tab.}
\makeatletter
\renewcommand{\chapterautorefname}{\textsection\@gobble}
\renewcommand{\sectionautorefname}{\textsection\@gobble}
\renewcommand{\subsectionautorefname}{\textsection\@gobble}
\renewcommand{\appendixautorefname}{\textsection\@gobble}



% --------------------
% Formatting tweaks
% --------------------
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}

\titleformat{\subsection}
  {\normalfont\large\bfseries}{\thesubsection}{1em}{}

\titleformat{\subsubsection}
  {\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}

\setlist[itemize]{noitemsep, topsep=4pt}

% --------------------
% Metadata
% --------------------
\title{Lab Manual}
\author{Roars Lab}
\date{Last updated: \today}

\begin{document}
\maketitle
\tableofcontents
\newpage


% ============================================================
\section{About the Lab}

\subsection{Lab mission and focus}
Research goals, scope, and ambitions.

\subsection{Lab philosophy and values}
Open science, rigor, transparency, reproducibility, etc.

\subsection{Lab history}
Founding, major changes, milestones.

\subsection{Lab space}
Physical description of the lab.



\subsection{Facilities}
The lab provides:
\begin{itemize}
  \item High-end desktops, laptops, and peripherals
  \item Shared GPU and compute servers
  \item Cloud and storage resources as needed
\end{itemize}

\subsection{Ethical code of conduct}

TBD

\section{Becoming a Lab Member}

\subsection{Online accounts}
Lab members are expected to maintain accounts on:
\begin{itemize}
  \item GitHub: you will need this to join Roars Lab's \href{https://code.roars.dev}{repositories and projects}.
  \item Discord: we use Discord for internal communication.
  \item Overleaf (optional): for collaborative writing.
\end{itemize}


\subsection{Required readings}
New members should read core papers relevant to their area and prior work from the lab.
Specific reading lists are project-dependent.

\subsection{Internal resources}
\begin{itemize}
  \item Lab servers
  \item Shared repositories
  \item Internal wikis and documentation
\end{itemize}



\subsection{External resources}

\subsubsection{VPN for Lab Servers} You will need VPN and Computing access to log into lab servers remotely. Send an email like below to \href{mailto:cechelp@gmu.edu}{cechelp@gmu.edu} and also CC the PI. 

\begin{tcolorbox}[enhanced]
\textbf{Subject}: VPN and Computing Access (Mesa AD Groups)
\\
{\small
Dear CECHelp, 
I am writing to request that my NetID (\textbf{you\_user\_name}) be added to the Active Directory groups listed below.
Groups requested for addition:
\begin{quote}
    CN=VS-GRA,OU=HelpDeskManagement,OU=VolgenauSchool...\\
    CN=VS-SR-VPN,OU=HelpDeskManagement,OU=VolgenauSchool...
\end{quote}
I have copied my advisor/supervisor, Professor Thanhvu Nguyen, on this email should you require confirmation that this access is necessary.
Thank you for your time and assistance with this.
...
}
\end{tcolorbox}


\subsubsection{Connecting to Wifi \texttt{Eduroam}}
\begin{itemize}
\item \url{https://its.gmu.edu/knowledge-base/eduroam/}
\end{itemize}

\paragraph{Linux} \url{https://its.gmu.edu/knowledge-base/how-to-set-up-eduroam-on-linux/}
\begin{itemize}
  \item Select \texttt{eduroam} from the list of available wireless networks.
  \item Configure the following settings:
  \begin{itemize}
    \item Wi-Fi security: WPA \& WPA2 Enterprise
    \item Authentication: Protected EAP (PEAP)
    \item Anonymous: leave this blank
    \item Domain: \texttt{gmu.edu}
    \item Check No CA certificate is required
    \item PEAP version: Automatic
    \item Inner Authentication: MSCHAPv2
    \item Username: Your FULL George Mason email address (e.g., \texttt{netid@gmu.edu})
    \item Password: Your Patriot Password
  \end{itemize}
\item Finally, click \texttt{Connect}. You should now be connected to \texttt{eduroam}.
\end{itemize}

% ============================================================
\section{Being a Lab Member}

\subsection{Roles and Duties}

\subsubsection{Roles}
Roles exist mainly for clarity, not hierarchy.

\subsubsection{Full members}
PI, PhD students, MS students, and undergraduate researchers.

\subsubsection{Associated members}
Visitors and collaborators working on shared projects.

\subsubsection{Non-scientific members}
Administrative staff and coordinators as applicable.

\subsubsection{Duties and responsibilities}
All members are expected to:
\begin{itemize}
  \item Own their projects
  \item Help others when possible
  \item Contribute to a healthy lab environment
\end{itemize}

\subsection{Career Development}

\subsubsection{Mentoring}
Mentoring is individualized.
Expectations increase with seniority.
Letters of recommendation require advance notice and evidence of work.

\subsection{How We Do Things}

\subsubsection{Time management}

\paragraph{Annual structure}
The lab follows the academic calendar, with flexibility outside major deadlines.

\paragraph{Leave and holidays}
Take time off when needed.
Outside deadlines, no approval is required for short breaks.

\paragraph{Lab hours}
There are no fixed working hours.
Productivity matters more than presence.

\paragraph{Absences}
Extended absences should be communicated.

\paragraph{Meetings}
Weekly lab meetings are standard.
Everyone speaks; no one hides.

\paragraph{Deadlines}
Deadlines are taken seriously.
Work intensifies near submissions and relaxes afterward.

\paragraph{Remote work}
Remote work is acceptable as long as progress is made.

\paragraph{Calendar usage}
Use calendars sensibly for meetings and deadlines.

\paragraph{Social events}
Social events happen organically.
No attendance is mandatory.

\subsection{Communication}

\subsubsection{Conflict resolution}
Conflicts should be addressed early and directly.
The PI will step in when needed.

\subsubsection{Internal communication}
Discord is primary.
Email is for official matters.

\subsubsection{External communication}
Public communication should reflect well on the lab.

\subsubsection{Collaborators}
External collaborations should be transparent.
When unsure, keep the PI in the loop.





\subsubsection{Life in the lab}
Be considerate about noise, space, and shared resources.

\subsubsection{Guests}
Guests require permission and must follow safety rules.

% ============================================================
\section{Dealing with Mistakes}

\subsection{General principles}
Mistakes happen.
Report them early.
Fix what can be fixed and learn from them.

\subsection{Confidentiality breaches}
Report immediately to the PI.

\subsection{Troubleshooting}
Document failures.
Reproduce issues.
Do not hide problems.

% ============================================================
\section{Maintaining Health and Safety}

\subsection{Health and safety}
Follow institutional safety procedures.
Seek help when sick or overwhelmed.

\subsection{Healthy lab life}
Burnout is not a virtue.
Support each other.

% ============================================================
\section{Leaving the Lab}

\subsection{Contacts and timeline}
Discuss plans early.

\subsection{Access revocation}
Accounts and access will be revoked after departure.

\subsection{Letters of recommendation}
Request well in advance and provide materials.

\subsection{Future steps}
The PI will assist with career transitions when possible.

\subsection{Keeping in touch}
Former members are encouraged to stay in contact.

% ============================================================
\section{Preparing a Study}

\subsection{Initiating a Study}

\subsubsection{Starting a new project}
Projects require PI approval.

\subsubsection{Project team}
Teams are small and flexible.

\subsubsection{Project logging}
All projects must have a documented home.

\subsection{Feasibility and Validity}

\subsubsection{Consultation}
Do literature reviews before committing.

\subsubsection{Cross-checking}
Test assumptions early.

\subsubsection{Pilot testing}
Pilot when appropriate.

\subsection{Operational Steps}

\subsubsection{Preregistration}
Used when appropriate.

\subsubsection{Approvals}

\paragraph{IRB approval}
Required for human-subject research.

\paragraph{Other approvals}
As needed.

\subsubsection{Data management plan}
Required for funded projects.

\subsubsection{Time management plan}
Milestones should be explicit.

\subsubsection{Materials and equipment}
Plan ahead.

\subsubsection{Experiment implementation}
Use lab-standard tools when possible.

\subsubsection{Testing space}
Coordinate shared resources.

% ============================================================
\section{Conducting a Study}

\subsection{Recruitment}
Follow approved protocols.

\subsection{Equipment use}
Training may be required.

\subsection{Data collection}
Follow documented procedures.

\subsection{Protocol compliance}
Checklists are encouraged.

\subsection{Documentation}
Log decisions and deviations.

\subsection{Closing data collection}
Archive and summarize.

% ============================================================
\section{Data and File Management}

\subsection{Data processing and analysis}
Analysis must be reproducible.

\subsection{Quality control}
Code should be readable and maintainable.

\subsection{Metadata}
Use codebooks and documentation.

\subsection{Standards}

\subsubsection{Dataset structure}
Prefer tidy, well-structured formats.

\subsubsection{Folder structure}
Separate raw and processed data.

\subsubsection{Naming conventions}
Be consistent.

\subsubsection{File formats}
Use open formats when possible.

\subsubsection{Version control}
Git is strongly encouraged.

\subsubsection{Archiving}
Archive all final artifacts.

\subsubsection{Data privacy}
Protect sensitive data.

\subsubsection{Sharing and access}
Follow open science norms when possible.

\subsubsection{Intellectual property}
Follow institutional IP policies.

% ============================================================
\section{Communicating Results}

\subsection{Reporting standards}
Follow community guidelines.

\subsection{Plotting and visualization}
Clarity over decoration.

\subsection{Writing papers}
Overleaf is standard.

\subsection{Proofreading}
Peer review within the lab is encouraged.

\subsection{Choosing venues}
Quality over quantity.

\subsection{Accreditation}

\subsubsection{Contributorship}
Decide early and document.

\subsubsection{Acknowledgments}
Acknowledge funding and help.

\subsection{Open access}
Use preprints when appropriate.

\subsection{Posters}
Use clean, readable templates.

\subsection{Talks}
Practice matters.

\subsection{Public engagement}
Optional, but encouraged.

% ============================================================
\section{Funding and Budgeting}

\subsection{Lab funds}
The lab covers essential research expenses.

\subsection{Student funding}
Students are supported via grants, fellowships, or TA-ships.

\subsection{Grants and administration}
The PI handles grant administration with student input when needed.

% ============================================================
\section*{Contributors}
List of contributors to the lab manual.

\end{document}

https://brainscan.uwo.ca/about/equity_diversity_inclusion/A-Research-Lab-Manual-Template.pdf